Project Protocol

### 2019-10-18 protocol.Rmd
Model specification

@@

Interactions:

>>>>

Main Effects:
Spatial trend

@@

Interactions:
Design and Difficulty: The interaction between the perceived difficulty of evaluating hexagon tile maps and geographic maps will be included to measure whether particiants feel differently about the designs.

Spatial Trend and Difficulty: The interaction between the spatial trend used in the lineup of hexagon tile maps and geographic maps will be included to measure whether particiants feel differently about finding different spatial trends.
